Lifting CDCL to Numerical Domains

### 2016-10-09 domains.tex
minor

APRON library is specialized for the abstract interpretation 
framework which does not require complementation property.  
To this end, we implement our own template-based 
interval, octagon and equality domains which supports 
complementation operator.  For example, the octagon in 
Figure~\ref{octagon} can be written as a conjunction of:
\[(x>=-2) \land (x<=1) \land (y>=-1) \land (y<=2) \land (x+y<=2) \land (x-y<=1) \land (y-x<=3) \land (-x-y<=2)\] 
The complementation of the above octagon can be written as disjunction of:
\[(x<-2) \lor (x>1) \lor (y<-1) \lor (y>2) \lor (x+y>2) \lor (x-y>1) \lor (y-x>3) \lor (-x-y>2)\]

>>>>

APRON library is specialized for the abstract interpretation 
framework which does not require complementation property.  
To this end, we implement our own template-based 
interval, octagon and equality domains which supports 
complementation operator.  
%For example, the octagon in Figure~\ref{octagon} can be written as a conjunction of:
%\[(x>=-2) \land (x<=1) \land (y>=-1) \land (y<=2) \land (x+y<=2) \land (x-y<=1) \land (y-x<=3) \land (-x-y<=2)\] 
For example, the complementation of the octagon in Figure~\ref{octagon} can be written as disjunction of:
\[(x<-2) \lor (x>1) \lor (y<-1) \lor (y>2) \lor (x+y>2) \lor (x-y>1) \lor (y-x>3) \lor (-x-y>2)\]
